XRONOS: an open data infrastructure for archaeological chronology

### 2024-12-05 paper.tex
Fix table width
Add missing references

\begin{longtable}{>{\raggedright\arraybackslash}p{\dimexpr 0.33\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedleft\arraybackslash}p{\dimexpr 0.33\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedright\arraybackslash}p{\dimexpr 0.33\linewidth -2\tabcolsep-1.5\arrayrulewidth}}

@@

\toprule
Issue & N & Description \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{>{\raggedright\arraybackslash}m{1.32\linewidth}}{Sites} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MISSING\_COORDINATES & 4452 & Missing geographic coordinates \\ 
INVALID\_COORDINATES & 0 & Geographic coordinates fall outside the earth's ellipsoid \\ 
MISSING\_COUNTRY\_CODE & 1221 & Missing data on what country the site is in \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{>{\raggedright\arraybackslash}m{1.32\linewidth}}{Samples} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MISSING\_MATERIAL & 138177 & Missing data on the sample material \\ 
MISSING\_TAXON & 138182 & Missing data on the sample taxon \\ 
MISSING\_CRS & 0 & Sample has coordinates but the coordinate reference system is not given \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{>{\raggedright\arraybackslash}m{1.32\linewidth}}{Taxons} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
UNKNOWN\_TAXON & 9260 & Sample taxon has not been matched to the GBIF Backbone Taxonomy \\ 
LONG\_TAXON & 509 & Description of the sample taxon is implausibly long \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{>{\raggedright\arraybackslash}m{1.32\linewidth}}{Radiocarbon dates} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MISSING\_C14\_AGE & 447 & Missing radiocarbon age \\ 
VERY\_OLD\_C14 & 76 & Radiocarbon age older than the effective range of the method (50 ka) \\ 
MISSING\_C14\_ERROR & 585 & Missing measurement error \\ 
MISSING\_D14C & 238875 & Missing δ13C measurement \\ 
MISSING\_D14C\_ERROR & 238875 & Missing δ13C measurement error \\ 
MISSING\_C14\_METHOD & 242233 & Missing data on radiocarbon dating method (conventional, AMS, etc.) \\ 
MISSING\_C14\_LAB\_ID & 1233 & Missing laboratory identifier \\ 
INVALID\_LAB\_ID & 16053 & Laboratory identifier does not match the standard format (e.g. 'Abc-1234') \\ 
MISSING\_C14\_LAB & 350190 & Missing data on the radiocarbon laboratory \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{>{\raggedright\arraybackslash}m{1.32\linewidth}}{Bibliographic references} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MIXED\_REFERENCE & 21933 & Bibliographic reference appears to combine multiple publications \\ 
MISSING\_BIBTEX & 42109 & Bibliographic reference without structured data in BibTeX format \\ 
\bottomrule

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{table}

@@

\fontsize{9.8pt}{11.7pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}>{\raggedright\arraybackslash}p{\dimexpr 0.30\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedleft\arraybackslash}p{\dimexpr 0.20\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedright\arraybackslash}p{\dimexpr 0.50\linewidth -2\tabcolsep-1.5\arrayrulewidth}}
\toprule
Issue & N & Description \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{l}{Sites} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MISSING\_COORDINATES & 4452 & Missing geographic coordinates \\ 
INVALID\_COORDINATES & 0 & Geographic coordinates fall outside the earth's ellipsoid \\ 
MISSING\_COUNTRY\_CODE & 1221 & Missing data on what country the site is in \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{l}{Samples} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MISSING\_MATERIAL & 138177 & Missing data on the sample material \\ 
MISSING\_TAXON & 138182 & Missing data on the sample taxon \\ 
MISSING\_CRS & 0 & Sample has coordinates but the coordinate reference system is not given \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{l}{Taxons} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
UNKNOWN\_TAXON & 9260 & Sample taxon has not been matched to the GBIF Backbone Taxonomy \\ 
LONG\_TAXON & 509 & Description of the sample taxon is implausibly long \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{l}{Radiocarbon dates} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MISSING\_C14\_AGE & 447 & Missing radiocarbon age \\ 
VERY\_OLD\_C14 & 76 & Radiocarbon age older than the effective range of the method (50 ka) \\ 
MISSING\_C14\_ERROR & 585 & Missing measurement error \\ 
MISSING\_D14C & 238875 & Missing δ13C measurement \\ 
MISSING\_D14C\_ERROR & 238875 & Missing δ13C measurement error \\ 
MISSING\_C14\_METHOD & 242233 & Missing data on radiocarbon dating method (conventional, AMS, etc.) \\ 
MISSING\_C14\_LAB\_ID & 1233 & Missing laboratory identifier \\ 
INVALID\_LAB\_ID & 16053 & Laboratory identifier does not match the standard format (e.g. 'Abc-1234') \\ 
MISSING\_C14\_LAB & 350190 & Missing data on the radiocarbon laboratory \\ 
\midrule\addlinespace[2.5pt]
\multicolumn{3}{l}{Bibliographic references} \\[2.5pt] 
\midrule\addlinespace[2.5pt]
MIXED\_REFERENCE & 21933 & Bibliographic reference appears to combine multiple publications \\ 
MISSING\_BIBTEX & 42109 & Bibliographic reference without structured data in BibTeX format \\ 
\bottomrule
\end{tabular*}

\end{table}%

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

@@

\bibitem[\citeproctext]{ref-Al-Abyadh-Balghelam-Dalma-JebelEtAl}
Al-Abyadh-Balghelam-Dalma-Jebel, A., Dhanna-Marawah-Marawah, M.R., Yas,
R.G.-R.-S.B., n.d. {ADIAS Radiocarbon Archive}.

\bibitem[\citeproctext]{ref-Alcantara2021}
Alcántara, A., 2021. Entre tepalcates. {Hacia} una comprensi{ó}n
historiogr{á}fica de la dataci{ó}n arqueom{é}trica en la arqueolog{í}a
mexicana (1950-2020) (PhD thesis).
\url{https://doi.org/10.13140/RG.2.2.24447.74400/2}

@@

\bibitem[\citeproctext]{ref-AndersonEtAl2010}
Anderson, D.G., Miller, D.S., Yerka, S.J., Gillam, J.C., Johanson, E.N.,
Anderson, D.T., Goodyear, A.C., Smallwood, A.M., 2010.
\href{https://www.jstor.org/stable/40914542}{{PIDBA} ({Paleoindian
Database} of the {Americas}) 2010: {Current Status} and {Findings}}.
Archaeology of Eastern North America 38, 63--89.

@@

\bibitem[\citeproctext]{ref-BANADORA}
Banque {Nationale} de {Donn{é}es} {Radiocarbone} ({BANADORA}), n.d.

\bibitem[\citeproctext]{ref-BarceloAlvarezEtAl2013}
Barceló Álvarez, J.A., Bogdanović, I., Capuzzo, G., 2013. New
developments of tecnological and archaeological data bases: {The}
example of radiocarbon dating, in: Arqueolog{í}a: {Actas} Del {Primer
Congreso Internacional} de {Buenas Pr{á}cticas} En {Patrimonio Mundial},
2013, {ISBN} 978-84-941030-9-4, p{á}gs. 733-749. JAS Arqueolog{í}a, pp.
733--749.

@@

\bibitem[\citeproctext]{ref-Benz2010}
Benz, M., 2010. {PPND} -- {The Platform} for {Neolithic Radiocarbon
Dates}.

@@

\bibitem[\citeproctext]{ref-BohnerSchyle2004}
Böhner, U., Schyle, D., 2004. Radiocarbon {CONTEXT} database.

@@

\bibitem[\citeproctext]{ref-BronkRamseyEtAl2009}
Bronk Ramsey, C., Higham, T.F.G., Brock, F., Baker, D., Ditchfield, P.,
2009. Radiocarbon {Dates} from the {Oxford Ams System}: {Archaeometry
Da}TEList 33. Archaeometry 51, 323--349.
\url{https://doi.org/10.1111/j.1475-4754.2008.00457.x}

@@

\bibitem[\citeproctext]{ref-Capriles2023}
Capriles, J.M., 2023. The {Bolivian Radiocarbon Database}: {A
Countrywide Compilation} of {Radiocarbon Dates}. Journal of Open
Archaeology Data 11. \url{https://doi.org/10.5334/joad.104}

\bibitem[\citeproctext]{ref-CapuzzoEtAl2014}
Capuzzo, G., Boaretto, E., Barceló, J.A., 2014. {EUBAR}: {A Database} of
{14C Measurements} for the {European Bronze Age}. {A Bayesian Analysis}
of {14C-Dated Archaeological Contexts} from {Northern Italy} and
{Southern France}. Radiocarbon 56, 851--869.
\url{https://doi.org/10.2458/56.17453}

\bibitem[\citeproctext]{ref-IRDD}
Chapple, R.M., 2019. Catalogue of {Radiocarbon Determinations} \&
{Dendrochronology Dates} ({August} 2019 release).

@@

\bibitem[\citeproctext]{ref-CochraneEtAl2021}
Cochrane, E.E., Rieth, T.M., Filimoehala, D., 2021. The first
quantitative assessment of radiocarbon chronologies for initial pottery
in {Island Southeast Asia} supports multi-directional {Neolithic}
dispersal. PLOS ONE 16, e0251407.
\url{https://doi.org/10.1371/journal.pone.0251407}

\bibitem[\citeproctext]{ref-CourtneyMustaphi2016}
Courtney Mustaphi, C., 2016. Radiocarbon dates from eastern {Africa} in
the {CARD2}.0 format. \url{https://doi.org/10.7910/DVN/NJLNRJ}

@@

\bibitem[\citeproctext]{ref-CremaEtAl2016}
Crema, E.R., Habu, J., Kobayashi, K., Madella, M., 2016. Summed
{Probability Distribution} of {14C Dates Suggests Regional Divergences}
in the {Population Dynamics} of the {Jomon Period} in {Eastern Japan}.
PLoS One 11, e0154809.
\url{https://doi.org/10.1371/journal.pone.0154809}

\bibitem[\citeproctext]{ref-dErricoEtAl2011}
d'Errico, F., Banks, W.E., Vanhaeren, M., Laroulandie, V., Langlais, M.,
2011. {PACEA Geo-Referenced Radiocarbon Database}. PaleoAnthropology
2011, 1--12.

@@

\bibitem[\citeproctext]{ref-deSaulieuEtAl2017}
de Saulieu, G., Oslisly, R., Nlend, P., Garcin, Y., Chevillotte, H.,
Kuete, N., 2017. Plateforme des datations arch{é}ologiques d'{Afrique
Centrale}. Version 2, 03.

\bibitem[\citeproctext]{ref-DeeEtAl2013}
Dee, M., Wengrow, D., Shortland, A., Stevenson, A., Brock, F., Girdland
Flink, L., Bronk Ramsey, C., 2013. An absolute chronology for early
{Egypt} using radiocarbon dating and {Bayesian} statistical modelling.
Proceedings of the Royal Society A: Mathematical, Physical and
Engineering Sciences 469, 20130395.
\url{https://doi.org/10.1098/rspa.2013.0395}

\bibitem[\citeproctext]{ref-DeeEtAl2012}
Dee, M.W., Rowland, J.M., Higham, T.F.G., Shortland, A.J., Brock, F.,
Harris, S.A., Ramsey, C.B., 2012. Synchronising radiocarbon dating and
the {Egyptian} historical chronology by improved sample selection.
Antiquity 86, 868--883. \url{https://doi.org/10.1017/S0003598X00047979}

\bibitem[\citeproctext]{ref-Diaz-RodriguezEtAl2023}
Díaz-Rodríguez, M., Nielsen, T.K., Maier, A., Riede, F., 2023. An
{Annotated Compilation} of {Chronometric Dates} for the {Middle-Upper
Palaeolithic Transition} (45-30 ka {BP}) in {Northern Iberia} ({Spain}).
Journal of Open Archaeology Data 11.
\url{https://doi.org/10.5334/joad.113}

@@

\bibitem[\citeproctext]{ref-DouglassEtAl2019}
Douglass, K., Hixon, S., Wright, H.T., Godfrey, L.R., Crowley, B.E.,
Manjakahery, B., Rasolondrainy, T., Crossland, Z., Radimilahy, C., 2019.
A critical review of radiocarbon dates clarifies the human settlement of
{Madagascar}. Quat. Sci. Rev. 221, 105878.
\url{https://doi.org/10.1016/j.quascirev.2019.105878}

@@

\bibitem[\citeproctext]{ref-FlohrEtAl2016}
Flohr, P., Fleitmann, D., Matthews, R., Matthews, W., Black, S., 2016.
Evidence of resilience to past climate change in {Southwest Asia}:
{Early} farming communities and the 9.2 and 8.2 ka events. Quat. Sci.
Rev. 136, 23--39. \url{https://doi.org/10.1016/j.quascirev.2015.06.022}

@@

\bibitem[\citeproctext]{ref-GarnettEtAl2023}
Garnett, M.H., Bryant, C.L., Freeman, S.P.H.T., Gulliver, P., Ascough,
P.L., 2023. A {DATABASE OF NERC RADIOCARBON MEASUREMENTS DETERMINED BY
ACCELERATOR MASS SPECTROMETRY}. Radiocarbon 1--4.
\url{https://doi.org/10.1017/RDC.2023.18}

\bibitem[\citeproctext]{ref-GayoEtAl2015}
Gayo, E.M., Latorre, C., Santoro, C.M., 2015. Timing of occupation and
regional settlement patterns revealed by time-series analyses of an
archaeological radiocarbon database for the {South-Central Andes}
(16{\(^\circ\)}--25{\(^\circ\)}{S}). Quaternary International,
Palaeodemography in {Southern South America} 356, 4--14.
\url{https://doi.org/10.1016/j.quaint.2014.09.076}

@@

\bibitem[\citeproctext]{ref-GillespieEtAl1984}
Gillespie, R., Gowlett, J.a.J., Hall, E.T., Hedges, R.E.M., 1984.
Radiocarbon {Measurement} by {Accelerator Mass Spectrometry}: {An Early
Selection} of {Dates}. Archaeometry 26, 15--20.
\url{https://doi.org/10.1111/j.1475-4754.1984.tb00313.x}

\bibitem[\citeproctext]{ref-GregoriodeSouza2020}
Gregorio de Souza, J., 2020. Rxpand: {Radiocarbon} dates for the spread
of farming and ceramics in tropical {South America}.

\bibitem[\citeproctext]{ref-GrossmannEtAl2023}
Großmann, R., Weinelt, M., Müller, J., 2023. Demographic dynamics
between 5500 and 3500 {calBP} (3550--1550 {BCE}) in selected study
regions of {Central Europe} and the role of regional climate influences.
PLOS ONE 18, e0291956.
\url{https://doi.org/10.1371/journal.pone.0291956}

@@

\bibitem[\citeproctext]{ref-HoebeEtAl2023}
Hoebe, P.W., Peeters, J.H.M., Arnoldussen, S., 2023. Parsing prehistoric
patterns: {Prospects} and limitations of a big radiocarbon dataset for
understanding the impact of climate on {Late Palaeolithic} and
{Mesolithic} populations in northwest {Europe} (16--7.5~ka {calBP}).
Journal of Archaeological Science: Reports 49, 103944.
\url{https://doi.org/10.1016/j.jasrep.2023.103944}

\bibitem[\citeproctext]{ref-HoggarthEtAl2021}
Hoggarth, J.A., Ebert, C.E., Castelazo-Calva, V.E., 2021. {MesoRAD}: {A
New Radiocarbon Data Set} for {Archaeological Research} in
{Mesoamerica}. Journal of Open Archaeology Data 9, 10.
\url{https://doi.org/10.5334/joad.83}

\bibitem[\citeproctext]{ref-HuetEtAl2024}
Huet, T., Basílio, A.C., Carvalho, A.F., Cubas, M., Gibaja, J.F.,
López-Romero, E., Oms, F.X., Mazzucco, N., 2024. {NeoNet Atlantic}.
{Radiocarbon Dates} for the {Late Mesolithic}/{Early Neolithic
Transition} in the {Southern European Atlantic Coast} 12, 2.
\url{https://doi.org/10.5334/joad.120}

\bibitem[\citeproctext]{ref-HuetEtAl2022}
Huet, T., Cubas, M., Gibaja, J.F., Oms, F.X., Mazzucco, N., 2022.
{NeoNet Dataset}. {Radiocarbon Dates} for the {Late Mesolithic}/{Early
Neolithic Transition} in the {North Central-Western Mediterranean
Basin}. Journal of Open Archaeology Data 10, 3.
\url{https://doi.org/10/gpk67w}

@@

\bibitem[\citeproctext]{ref-KellyEtAl2022}
Kelly, R.L., Mackie, M.E., Robinson, E., Meyer, J., Berry, M.,
Boulanger, M., Codding, B.F., Freeman, J., Garland, C.J., Gingerich, J.,
Hard, R., Haug, J., Martindale, A., Meeks, S., Miller, M., Miller, S.,
Perttula, T., Railey, J.A., Reid, K., Scharlotta, I., Spangler, J.,
Thomas, D.H., Thompson, V., White, A., 2022. A {New Radiocarbon
Database} for the {Lower} 48 {States}. American Antiquity 87, 581--590.
\url{https://doi.org/10.1017/aaq.2021.157}

@@

\bibitem[\citeproctext]{ref-KimEtAl2021}
Kim, H., Lee, G.-A., Crema, E.R., 2021. Bayesian analyses question the
role of climate in {Chulmun} demography. Scientific Reports 11, 23797.
\url{https://doi.org/10.1038/s41598-021-03180-4}

@@

\bibitem[\citeproctext]{ref-Kudo2018}
Kudo, Y., 2018. Approach for {Creating Database} of the {Radiocarbon
Dates Published} on the {Archaeological Research Reports} in {Japan}.
Bulletin of the National Museum of Japanese History 212, 251.

\bibitem[\citeproctext]{ref-KudoEtAl2023}
Kudo, Y., Sakamoto, M., Hakozaki, M., Stevens, C.J., Crema, E.R., 2023.
An {Archaeological Radiocarbon Database} of {Japan}. Journal of Open
Archaeology Data 11. \url{https://doi.org/10.5334/joad.115}

@@

\bibitem[\citeproctext]{ref-LinnenluckeEtAl2023}
Linnenlucke, L., Bird, M.I., Petchey, F., Alliston, G., McNiven, I.J.,
David, B., Ulm, S., 2023. Assessing the {Reliability} of a {Small-Scale
Legacy Radiocarbon Dataset Using Chronometric Transparency Approaches}:
{Torres Strait Radiocarbon Database}. Journal of Open Archaeology Data
11. \url{https://doi.org/10.5334/joad.95}

\bibitem[\citeproctext]{ref-Lipo2020}
Lipo, C., 2020. A repository of radiocarbon data for {Rapa Nui}.

@@

\bibitem[\citeproctext]{ref-LucariniEtAl2020}
Lucarini, G., Wilkinson, T., Crema, E.R., Palombini, A., Bevan, A.,
Broodbank, C., 2020. The {MedAfriCarbon Radiocarbon Database} and {Web
Application}. {Archaeological Dynamics} in {Mediterranean Africa}, ca.
9600--700 {BC}. Journal of Open Archaeology Data 8.
\url{https://doi.org/10.5334/joad.60}

@@

\bibitem[\citeproctext]{ref-ManningEtAl2016}
Manning, K., Colledge, S., Crema, E., Shennan, S., Timpson, A., 2016.
The {Cultural Evolution} of {Neolithic Europe}. {EUROEVOL Dataset} 1:
{Sites}, {Phases} and {Radiocarbon Data}. Journal of Open Archaeology
Data 5, 275. \url{https://doi.org/10.5334/joad.40}

@@

\bibitem[\citeproctext]{ref-Martinez-GrauEtAl2021}
Martínez-Grau, H., Morell-Rovira, B., Antolín, F., 2021. Radiocarbon
{Dates Associated} to {Neolithic Contexts} ({Ca}. 5900 -- 2000 {Cal BC})
from the {Northwestern Mediterranean Arch} to the {High Rhine Area}.
Journal of Open Archaeology Data 9.
\url{https://doi.org/10.5334/joad.72}

\bibitem[\citeproctext]{ref-McFadgenEtAl2000}
McFadgen, B., Higham, T., Sparks, R.J., 2000. New {Zealand} radiocarbon
database for archaeology. Archaeology in New Zealand 43, 297--300.

@@

\bibitem[\citeproctext]{ref-PalmisanoEtAl2022}
Palmisano, A., Bevan, A., Kabelindde, A., Roberts, N., Shennan, S.,
2022a. {AIDA}: {Archive} of {Italian} radiocarbon {DAtes}.

\bibitem[\citeproctext]{ref-PalmisanoEtAl2022a}
Palmisano, A., Bevan, A., Lawrence, D., Shennan, S., 2022b. The {NERD
Dataset}: {Near East Radiocarbon Dates} between 15,000 and 1,500 cal.
Yr. {BP} 10, 2. \url{https://doi.org/10.5334/joad.90}

\bibitem[\citeproctext]{ref-PalmisanoEtAl2017}
Palmisano, A., Bevan, A., Shennan, S., 2017. Data and code for
demographic trends in the paper "{Human} responses and non-responses to
climatic variations during the {Last Glacial-Interglacial} transition in
the eastern {Mediterranean}".
\url{https://doi.org/10.14324/000.ds.1570274}

\bibitem[\citeproctext]{ref-Pardo-GordoEtAl2023}
Pardo-Gordó, S., Vidal-Matutano, P., González-Marrero, M. del C.,
Chávez-Álvarez, M.E., 2023. The {14Canarias} web application. {An}
interactive radiocarbon database for the {Canary Islands}. Journal of
Open Archaeology Data 11. \url{https://doi.org/10.5334/joad.105}

\bibitem[\citeproctext]{ref-Perrin2019}
Perrin, T., 2019. \href{https://www.jstor.org/stable/26910790}{{BDA}:
Une {Base} de {Donn{é}es Arch{é}ologique} collaborative en ligne}.
Bulletin de la Soci{é}t{é} pr{é}historique fran{ç}aise 116, 159--162.

\bibitem[\citeproctext]{ref-PetcheyEtAl2022}
Petchey, F., Bickler, S., Hughes, L., Bunbury, M., 2022. The
{Aotearoa}/{New Zealand Radiocarbon Database Upgrade}. Archaeology in
New Zealand 65, 32--40.

@@

\bibitem[\citeproctext]{ref-Rademaker2024}
Rademaker, K., 2024. Updated {Peru} archaeological radiocarbon database,
20,000--7000 {14C BP}. Quaternary International.
\url{https://doi.org/10.1016/j.quaint.2024.01.012}

\bibitem[\citeproctext]{ref-RademakerEtAl2013}
Rademaker, K., Bromley, G.R.M., Sandweiss, D.H., 2013. Peru
archaeological radiocarbon database, 13,000--7000 {14C B}.{P}.
Quaternary International, A {Late Pleistocene}/early {Holocene}
archaeological {14C} database for {Central} and {South America}:
Palaeoenvironmental contexts and demographic interpretations 301,
34--45. \url{https://doi.org/10.1016/j.quaint.2012.08.2052}

@@

\bibitem[\citeproctext]{ref-RamseyEtAl2010}
Ramsey, C.B., Dee, M.W., Rowland, J.M., Higham, T.F.G., Harris, S.A.,
Brock, F., Quiles, A., Wild, E.M., Marcus, E.S., Shortland, A.J., 2010.
Radiocarbon-{Based Chronology} for {Dynastic Egypt}. Science 328,
1554--1557. \url{https://doi.org/10.1126/science.1189395}

\bibitem[\citeproctext]{ref-ReingruberThissen2017}
Reingruber, A., Thissen, L., 2017. The {14SEA Project}: {A 14C} database
for {Southeast Europe} and {Anatolia} (10,000--3000 {calBC}).

\bibitem[\citeproctext]{ref-ReingruberThissen2009}
Reingruber, A., Thissen, L., 2009. Depending on {14C Data}:
{Chronological Frameworks} in the {Neolithic} and {Chalcolithic} of
{Southeastern Europe}. Radiocarbon 51, 751--770.
\url{https://doi.org/10.1017/S0033822200056071}

@@

\bibitem[\citeproctext]{ref-Riris2021}
Riris, P., 2021. Carribean-{14C}: {A} compilation of 2147 anthropogenic
radiocarbon ({14C}) dates for the {Caribbean} region from 504 sites
across 57 islands.

@@

\bibitem[\citeproctext]{ref-SeidenstickerSchmid2021}
Seidensticker, D., Schmid, C., 2021. Dirkseidensticker/{aDRAC}: V2.0
{Pikunda}. \url{https://doi.org/10.5281/zenodo.4530717}

@@

\bibitem[\citeproctext]{ref-TanindiErdogu2005}
Tanindi, O., Erdoğu, B., 2005. Recording the past: Towards an inventory
of the archaeological sites of {Turkey}. Conservation and Management of
Archaeological Sites 7, 125--130.
\url{https://doi.org/10.1179/135050305793137468}

@@

\bibitem[\citeproctext]{ref-UriarteGonzalezEtAl2017}
Uriarte González, A., Fernández Freire, C., Fraguas Bravo, A., Castañeda
Clemente, N., Capdevila Montes, E., Salas Tovar, E., Gilman, A., Bosque
González, I. del, Vicent García, J.M., 2017. {IDEArq-C14: Una
Infraestructura de Datos Espaciales para la cronolog{í}a
radiocarb{ó}nica de la Prehistoria Reciente ib{é}rica}.
\url{https://doi.org/10.13039/501100003329}

\bibitem[\citeproctext]{ref-VanStrydonckDeRoock}
Van Strydonck, M., De Roock, E., n.d. Radiocarbon and stable isotope
measurements. Royal Institute for Cultural Heritage.

@@

\bibitem[\citeproctext]{ref-Vermeersch2024}
Vermeersch, P.M., 2024. Radiocarbon {Palaeolithic Europe Database}.

@@

\bibitem[\citeproctext]{ref-WangEtAl2014}
Wang, C., Lu, H., Zhang, J., Gu, Z., He, K., 2014. Prehistoric
demographic fluctuations in {China} inferred from radiocarbon data and
their linkage with climate change over the past 50,000 years. Quaternary
Science Reviews 98, 45--59.
\url{https://doi.org/10.1016/j.quascirev.2014.05.015}

\bibitem[\citeproctext]{ref-Weninger2022}
Weninger, B., 2022. {CalPal}.
\url{https://doi.org/10.5281/ZENODO.7215741}

@@

\bibitem[\citeproctext]{ref-WilliamsSmith2013}
Williams, A.N., Smith, M., 2013.
\href{https://www.jstor.org/stable/23621983}{{AustArch3}: {A} database
of 14 {C} and luminescence ages from archaeological sites in southern
{Australia}}. Australian Archaeology 102--102.

\bibitem[\citeproctext]{ref-WilliamsSmith2012}
Williams, A.N., Smith, M.A., 2012.
\href{https://www.jstor.org/stable/23621556}{{AustArch2}: {A} database
of 14 {C} and luminescence ages from archaeological sites in the {Top
End}}. Australian Archaeology 146--146.

\bibitem[\citeproctext]{ref-WilliamsEtAl2008}
Williams, A.N., Smith, M.A., Turney, C.S.M., Cupper, M.L., 2008.
\href{https://www.jstor.org/stable/20839288}{{AustArch1}: {A Database}
of {\(^{14}\)}{C} and {Luminescence Ages} from {Archaeological Sites} in
the {Australian Arid Zone}}. Australian Archaeology 99--99.
